### 2021-01-20 manuscript.tex
?

\begin{figure}[H]
    \includegraphics[width=\linewidth]{fig/rmarkdown_flow.png}
    \caption[Rmarkdown Rendering Flow]{\textbf{Rmarkdown Rendering Flow} The core web framework was created using a stitch process composed of two document conversion steps, which are both contained in the single \texttt{rmarkdow::render\_site} command. These two transformations are done by the R-specific knitr package and then the open-source pandoc tool. The first phase holds less relevance in particular as its role is to execute R code chunks, of which there are few in our site content. The markdown output from this step is seamlessly injected into a pandoc conversion which offers a large variety in document output. Specific to our case, the pandoc conversion paired with a companion yaml configuration file allows for multidocument markdown-to-html rendering which is assembled as a complete site stack. As a single process, this function generates an integrated, modern web front-end from content written in a light-weight syntax with almost none of the typical complexity of full-scale web page creation.}\label{fig:renderFlow}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/file_tree.png}
    \caption[Project Directory File Tree Comparison]{\textbf{Project Directory File Tree Comparison} The above figure offers a qualitative assessment of an element of technical debt that was improved in refactoring. Shown are the file trees of the site directories of the new and old projects. What is illustrated is a dramatic improvement in the tree size and complexity through the elimination of a large degree of content, log, and style files. This is accentuated even forther when comparing the source code. This was accomplished both in the intentional design of eliminating content redundancy and in the streamlined structure of the Rmarkdown rendering process. This allowed for the elimination of several dimensions of broader web design elements.}\label{fig:fileTree}
\end{figure}

@@

\subsection{Resource Utilization Improvements}
space constraints eliminated. Server resource reqs reduced overall.

>>>>

\begin{figure}[H]
    \includegraphics[width=\linewidth]{fig/rmarkdown_flow.png}
    \caption[Rmarkdown Rendering Flow]{\textbf{Rmarkdown Rendering Flow} The core web framework was created using a stitch process composed of two document conversion steps, which are both contained in the single \texttt{rmarkdow::render\_site} command. These two transformations are done by the R-specific knitr package and then the open-source pandoc tool. The first phase holds less relevance in particular as its role is to execute R code chunks, of which there are few in our page content. The markdown output from this step is seamlessly injected into a pandoc conversion which offers a large variety in document output. Specific to our case, the pandoc conversion paired with a companion yaml configuration file allows for multidocument markdown-to-html rendering which is assembled as a complete site stack. As a single process, this function generates an integrated, modern web front-end from content written in a light-weight syntax with almost none of the typical complexity of full-scale web page creation.}\label{fig:renderFlow}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/file_tree.png}
    \caption[Project Directory File Tree Comparison]{\textbf{Project Directory File Tree Comparison} The above figure offers a qualitative assessment of an element of technical debt that was improved in refactoring. Shown are the file trees of the site directories of the new and old projects. What is illustrated is a dramatic improvement in the tree size and complexity through the elimination of a large degree of content, log, and style files. This is accentuated even forther when comparing the source code. This was accomplished both in the intentional design of eliminating content redundancy and in the streamlined structure of the Rmarkdown rendering process. This allowed for the elimination of several dimensions of broader web design and table build data elements.}\label{fig:fileTree}
\end{figure}

@@

\subsection{Resource Utilization Improvements}
Space constraints eliminated. Server resource reqs reduced overall.

Interface now streamlined to single page instead of a bunch of pages.
